Global adjoint tomography -- Model GLAD-M25

### 2018-10-15 main.tex
fix typo
add asia section

{\color{Red} Wenjie: Read for Jeroen to edit}

@@

...to be done...
We presented our model GLAD-M25, with S362ANI+M, S40RTS and EARA2014.
At 100km depth, our model shows sharpening at the Himalayas subductions
zones. At 250km, our models shows the subduction in the east part.
At 400km, our models shows the subduction at sumartra.

>>>>

{\color{Red} Wenjie: Ready for Jeroen to edit}

@@

Asia has a very compliated tectonic settings, which mainly contains the interaction
among India, Euroasia, Australia, Pacific and Phillipine plates. Even though we don't
have a significant large number of high event-response stations at this region(compared
to Europe and North America), our inversion is compsentated by the large number of
temporary arrays and earthquakes.

The southwestern part of china is featured by the Himalayas mountain, which is 
a shallow expression of the collission between India and Euroasian plate. Our
models shows a strong high-velocity anomalies near the plate boundary, and this
anomaly has all the way extending from 100km to 600km depth. With the increase
of depth, the high-velcity regions get sharper, indicating the narrowing
root of subduction plate. The high-elevation Tibetan platuea, residenting to
the north of Himalaya monuntains, shows a relatively low velocity
comparing to its surroundings, including the Himalayas at its south and Titanshan
Mountain at is North.

The southern part of Asia sees the majority tectonic activity between the Phillipine
, EuroAsia and Australia plate. The Summatra and Java trench, shown as sharp high-velocity
anomaly in our models below 200km, nicely follows the boundary between Euroasia
and Australia plates. This feature stays still very sharp at the 600km and extend
down to 1000km. We will have more detailed discussion about it in the follwing sections.
The Malina and Philippine Trench is also much sharper in our model between 200km and
600km.
The eastern part has a series of trenchs, including Japan Trench, Izu-Bonin Trench,
Mariana Trench from North to the Sounth. All those features follows perfectly with
the plate boundary, from 200km to 400km depth, as emerging features
compared the two global models. At the north, our models shows low-velocity structures
, which could be associated with the Altay-Sayan and Baikai rift systems.

Other than the boundaries, our models also show much more details at the intra-plate
tectonic activities. Our models shows good correlation of low-velocity regions with
the Hainan spot and Changbai Volcanoes. Those low-velocity features is prominent at shallow
depth, but gradually reduce its magnitude down with the increase of depth, indicating
that those features might be lithospherical acticity rather than deep mantle's. The Sichuan
basin, shows as a very locolized high-velocity structures, is extended below 250km.
At 600, most of the models shows a large regions of high-velocities near the Phillipine
plate, which may indicate the pounding of ancient subucted plates.
